\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{LHS CS Team: Calendar 2016-2017}
\author{Captains: Vivek Bhupatiraju, Louie Golowich, Krishna Suraj}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

The 16 programming contest topics (list compiled by USACO Coaches). Note that this list is very old, and that the topics have shifted slightly in focus recently. The list we made on the next page reflects more current contest problems.
\begin{itemize}
\item Dynamic Programming
\item Greedy
\item Complete Search
\item Flood Fill
\item Shortest Path
\item Recursive Search Techniques
\item Minimum Spanning Tree
\item Knapsack
\item Computational Geometry
\item Network Flow
\item Eulerian Path
\item Two-Dimensional Convex Hull
\item BigNums
\item Heuristic Search
\item Approximate Search
\item Ad Hoc Problems
\end{itemize}

\newpage

Our list of topics:
\begin{itemize}
\item Algorithms
\begin{itemize}
\item Dynamic Programming
\item Graph Algorithms
\begin{itemize}
\item Breadth First Search / Depth First Search
\item Flood Fill
\item Shortest Path
\item Minimum Spanning Tree
\item Eulerian Path / Tour
\item Network Flow
\end{itemize}
\item Binary Search on Answer
\item Divide and Conquer
\item Tree Algorithms
\begin{itemize}
\item Level Ancestor
\item Lowest Common Ancestor / Range Min Query
\end{itemize}
\item String Algorithms
\begin{itemize}
\item Polynomial Hashing
\end{itemize}
\item Plane Sweep
\item Longest Increasing Subsequence / Minimum Number of Decreasing Subsequences
\item Computational Geometry
\begin{itemize}
\item Convex Hull
\end{itemize}
\end{itemize}
\item Data Structures
\begin{itemize}
\item Prefix Sums
\item Heaps / Priority Queues
\item Segment Trees
\item Fenwick Trees
\item Range Trees
\item Union Find
\item (Balanced) Binary Search Trees
\item Hash Tables
\end{itemize}
\end{itemize}

\newpage

Our calendar:
\begin{itemize}
\item September
% The basics
\begin{itemize}
\item Introduction.
\item Greedy and brute force algorithms.
\end{itemize}

\item October
% The essentials
\begin{itemize}
\item Basic graph algorithms.
\item Dynamic programming.
\end{itemize}

\item November
% Useful for gold
\begin{itemize}
\item Basic data structures.
\item Binary search.
\item Divide and conquer.
\end{itemize}

\item December
\begin{itemize}
\item USACO contest 1?
\item Contest practice.
\item More advanced graph algorithms.
\end{itemize}

\item January
% Some fun stuff
\begin{itemize}
\item USACO contest 2?
\item String algorithms.
\item Tree algorithms (level ancestor, lowest common ancestor / range min query).
\end{itemize}

\item February
% Getting serious
\begin{itemize}
\item USACO contest 3?
\item More advanced data structures.
\end{itemize}

\item March
% Platinum level
\begin{itemize}
\item Contest practice.
\item Hard or less common algorithms.
\item Very advanced data structures.
\end{itemize}

\item April
\begin{itemize}
\item USACO contest 4 (US Open)?
\end{itemize}

\item May

\item June

\end{itemize}


\end{document}  